\documentclass{report}

\title{ Western Museums Association Program Committee: Session Proposals (Round 1)}
\date{ Last updated: March 12, 2022}
\author{Western Museums Association}

\begin{document}
  \pagenumbering{gobble}
  \maketitle
  \newpage
  \tableofcontents
  \newpage
  \pagenumbering{arabic}
  
    \newpage
    \chapter*{ Regular session/panel (roundtable, single speaker, etc.) }

      
        
        
        
        
        
          \newpage
          \section{ Testing - Revised Again! }
            \begin{description}
              \item [ID:]
              WMA2022\_002

              \item [Assigned to:]Jacqueline Cabrera~
                \item [Track:]Technology~
              \end{description}

              Here\&rsquo;s my discription.

              \subsection*{Session Information}
                \begin{description}
                  \item [Format:] Regular session/panel (roundtable, single speaker, etc.)
							    
								  \item [Fee:]Nope
							     
							    \item [Uniqueness:]My session is bad-ass.
							    \item [Objectives:]THings people will learn is tomatoe.
							    \item [Engagement:]Engagement! 75 words!
							    \item [Relationship to Theme:]Here's the theme.
							    
                \end{description}
              \subsection*{Audience}
                \begin{description}
                  \item [Audiences:]Registrars, Collections Managers~
                  \item[Professional Level:]Museum board members~Senior Level~
                \item[Scalability:] Scale!

							
              \end{description}
            \subsection*{Participants}
              \subsubsection*{ Koven Smith }
              Submitter, Moderator, Presenter\newline
              Freelance Adventurer\newline
              Justice League, Akron, OH
              \newline
              koven.smith@gmail.com\newline
              koven@kovenjsmith.com\newline
              9178038432\newline

              whut\newline


              

              
                \subsubsection*{ Joey Joe Joe }
                Presenter\newline
                Amboy Duke\newline
                Ted Nugent, Fake Town, NJ
                \newline
                
                
                

                Justification for presenter 1
                \emph{ (confirmed) }
              

              
                \subsubsection*{ Pres 2 Pres 2 Last }
                Presenter\newline
                PRes 2 title\newline
                pres 2 institution, pres 2 city
                \newline
                pres2@email.com\newline
                pres2@example.com\newline
                pres2 tel\newline

                Why?
                \emph{ (not confirmed) }
              

              

              
    \newpage
    \chapter*{ Half-day workshop (9:00 a.m. – 1:00 p.m.) }

      
        
        
    \newpage
    \chapter*{ Full-day workshop (9:00 a.m. – 4:00 p.m.) }

      
        
        \end{document}
